# `ggplot2` error: object not found

```{r include=FALSE}
library(ggplot2)
```

## The issue

This error message happens when R is unable to find the data you specified to produce your plot.

## Reproducible error

The following code will replicate this error:

```{r eval=FALSE}
library(ggplot2)
ggplot(bananas, aes(monkey, eaten)) +
  geom_bar(stat = "identity")
```

In the above example, `bananas` does not exist. To make the code work, you must have a prior line of code that goes:

```{r eval=FALSE}
bananas = ...
# or
bananas <- ...
```

where `...` is whatever function is used to create a data object, such as `data.frame()` or `read.csv()`. 


## Suggested solution

Ensure that the data object has been created or defined. 
If you used the `read.csv()` (or similar) function, make sure the results are assigned to a name. 
Here, we assign the output of `data.frame()` to the object, `bananas`:

```{r}
bananas <- data.frame(monkey = c(1:5), eaten = c(2, 6, 3, 4, 7))
```

Since `bananas` is now an object that has been defined, then repeating the original code will now work:

```{r}
ggplot(bananas, aes(monkey, eaten)) +
  geom_bar(stat = "identity")
```

## Additional resources

- [What does “Error: object '<myvariable>' not found” mean?](https://stackoverflow.com/questions/27886839/what-does-error-object-myvariable-not-found-mean)
