# Data import: cannot open file: No such file or directory


## The issue

This error message occurs during data import. It is likely that an incorrect file path was provided in the `path = ` argument.


## Reproducible error

The following type of code will reproduce this error:

```{r eval=FALSE}
# either the folder `bananas`, or the file `apes.csv`, 
# or both, do not exist:
read_csv("bananas/apes.csv") 
```

## Suggested solution

**Step 1:** Move the data file into the same folder as your current .Rmd file. Then, the path to the file is simply the file name:

```{r eval=FALSE}
# not evaluated
read_csv("apes.csv") # `apes.csv` and your .Rmd file are in the same folder
```

<!-- **The code above may not work if you evaluate code outside of a knit** (i.e. you like to click on "Run" or use `cmd+return` or `ctrl+enter` on code). -->

**Step 2 (optional):** Change the global working directory to match your R Markdown file's working directory. 
This is for students who tend to evaluate code chunks without knitting (i.e. they like to click on "Run" or use `cmd+return` or `ctrl+enter` on code).
In the toolbar menu, click on **Session > Set Working Directory > To Source File Location**. 
Note that users may need to repeat Step 2 or restart their R session to reset the working directory for other projects.

## Additional resources

- [The working directory for R code chunks](https://bookdown.org/yihui/rmarkdown-cookbook/working-directory.html)
